Comparing variations in sediment transport capacity between subglacial and subaerial channels

### 2023-05-16 Delaney2023.tex
Rejected version by GRL

\title{Comparing variations in sediment transport capacity between subglacial and subaerial systems }

@@

\item The systems' divergence in transport capacity response may impact sediment dynamics at glacier margins and interpretation of sediment records.
\end{keypoints}

@@

  \begin{center}
    \begin{figure}[H]
      \includegraphics[width=0.65\linewidth]{Cartoon.pdf}
      \caption{Cartoon of the situation with various parameters. Water velocity magnitude in the subglacial, $v_g$, and subaerial, $v_f$, systems are shown by arrow length. $S_g$ and $S_f$ represent the cross-sectional area in subglacial and subaerial channels. The subglacial channel widths $w_{cg}$ remain steady, while the subaerial channel widths evolve $w_{cf}$, denoted by the thick black line. Shear stress $\tau$ is responsible for the mobilization of sediment and increases with the number of makers at the channel bed. 
        Note that in the subaerial channel parameterization, rectangular channel shapes are implemented (Section~\ref{sect:fluv}).} 
      \label{fig:cartoon}
    \end{figure}
  \end{center}

@@

  \begin{center}
    \begin{figure}[H]
      \includegraphics[width=0.7\linewidth]{model_outputs.pdf}
      \caption{Response of channel width (a), hydraulic diameter (b),  Reynolds number  (c),  water velocity (d), shear-stress (e), and width-integrated shear-stress (f)  to different water discharge values. The glacial system is in blue and the subaerial system is in green.  Horizontal bars in d, e, and f represent the range of values in the  output. Gray space represents water discharge below the mean value. }
      \label{fig:model_outs}
    \end{figure}
  \end{center}

@@

  \begin{center}
    \begin{figure}[H]
      \includegraphics[width=0.7\linewidth]{multi_run.pdf}
      \caption{Ratio of range of water velocity, shear-stress, and width integrated shear-stress for glacial and subaerial systems in response to mean water discharge (a, b, c), and  variability in water discharge (d, e, f).  
        Range  $\chi$ for each variable is given in Equation~\ref{eq:var}. Values greater than $1$ shown in white space are parameter combinations that vary more in a subglacial  system.
        Histograms (g-i) show the frequency of relative variations across variables in the parameterization.}
      \label{fig:range}
    \end{figure}
  \end{center}

@@

  Records of sediment discharge have been used to establish the relationship, or lack thereof, between sediment discharge and climate in glacial systems \, cite<e.g.>[]{koppes2009a,willenbring2016,mariotti2021}.
  The variability in subglacial sediment transport capacity presented here applies most generally to short-time scales responsible for the size of subglacial channels.
  Yet, identifying climatic signals in sediment transport from transport-limited glaciers may require higher thresholds of climatic perturbation compared to subaerial systems \cite{tofelde2021}.
  This higher threshold of climatic perturbation may persist in addition to the stochastic nature of erosion and deposition in fluvial environments \cite{castletort2003,jerolmack2010,romans2016}.
  For instance, sediment discharge records from two glaciers in the Swiss Alps show that $40$ to $50$\% of a season's sediment discharge occurs when water discharge is below the $75^{\mathrm{th}}$ quantile of the season \cite{delaney2018}.
  Such a large quantity of sediment transported at lower water discharges may occur in part because sediment transport capacity responds to the size of the glacier conduit, in addition to water discharge (Section~\ref{sect:sub_mode}).

@@

  These different characteristics between glacial and subaerial channels show that records of sediment transport downstream of glaciers capture both subglacial and subaerial processes together.
  Such processes might be particularly relevant at glacier margins, where water transitions from pressurized subglacial flow to open-channel subaerial flow.
  The inconsistent response of sediment transport in subglacial and subaerial systems to changing water discharge could add uncertainty in evaluating  sediment transport signals in subglacial systems.
  In addition, the subglacial parameterization shows that sediment transport capacity in glacier systems responds to a large number of factors such as channel size, ice thickness, and glacier surface slope, which may react to climate forcing differently than water discharge alone. 
  The differences in subglacial and subaerial channels' response to changing hydrology should be considered when examining sediment transport processes in glacierized catchments.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% 
% \bibliography{<name of your .bib file>} don't specify the file extension
% 
% don't specify bibliographystylei

@@

%\bibliography{Paperlib.bib}
\begin{thebibliography}{}

@@

\bibitem [\protect \citeauthoryear {%
Castelltort%
\ \BBA {} {Van Den Driessche}%
}{%
Castelltort%
\ \BBA {} {Van Den Driessche}%
}{%
{\protect \APACyear {2003}}%
}]{%
castletort2003}
\APACinsertmetastar {%
castletort2003}%
\begin{APACrefauthors}%
Castelltort, S.%
\BCBT {}\ \BBA {} {Van Den Driessche}, J.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2003}{}{}.
\newblock
{\BBOQ}\APACrefatitle {{How plausible are high-frequency sediment supply-driven
  cycles in the stratigraphic record?}} {{How plausible are high-frequency
  sediment supply-driven cycles in the stratigraphic record?}}{\BBCQ}
\newblock
\APACjournalVolNumPages{Sedimentary Geology}{157}{1}{3-13}.
\newblock
\begin{APACrefURL}
  \url{https://www.sciencedirect.com/science/article/pii/S0037073803000666}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1016/S0037-0738(03)00066-6} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\bibitem [\protect \citeauthoryear {%
Williams%
}{%
Williams%
}{%
{\protect \APACyear {1989}}%
}]{%
williams1989}
\APACinsertmetastar {%
williams1989}%
\begin{APACrefauthors}%
Williams, G\BPBI .%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{1989}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Sediment concentration versus water discharge during
  single hydrologic events in rivers} {Sediment concentration versus water
  discharge during single hydrologic events in rivers}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Journal of Hydrology}{111}{1}{89 -- 106}.
\newblock
\begin{APACrefURL}
  \url{http://www.sciencedirect.com/science/article/pii/0022169489902540}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1016/0022-1694(89)90254-0} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\begin{center}
  \begin{figure}[H]
    \includegraphics[width=0.7\linewidth]{multi_run_vars.pdf}
    \caption{Variability $\chi$ in velocity ($v_g$, $v_f$; a) shear stress ($\tau_g$, $\tau_f$; b) and width-integrated shear stress ($\tau_{tg}$, $\tau_{tf}$; c)  in glacial and subaerial systems. Across the parameter space in Figure~\ref{fig:range}. }
    \label{fig:gammas}
  \end{figure}
\end{center}

>>>>

\title{Comparing variations in sediment transport capacity between subglacial and subaerial channels }

@@

\item The systems' divergence in transport response may impact sediment dynamics at glacier margins and interpretation of sediment records.
\end{keypoints}

@@

  \begin{center}
    \begin{figure}[H]
      \includegraphics[width=0.8\linewidth]{Fig1.pdf}
      \caption{Cartoon of the situation with various parameters. Water velocity magnitude in the subglacial, $v_g$, and subaerial, $v_f$, systems are shown by arrow length. $S_g$ and $S_f$ represent the cross-sectional area in subglacial and subaerial channels. The subglacial channel widths $w_{cg}$ remain steady, while the subaerial channel widths evolve $w_{cf}$, denoted by the thick black line. Shear stress $\tau$ is responsible for the mobilization of sediment and increases with the number of makers at the channel bed. 
        Note that in the subaerial channel parameterization, rectangular channel shapes are implemented (Section~\ref{sect:fluv}).} 
      \label{fig:cartoon}
    \end{figure}
  \end{center}

@@

  \begin{center}
    \begin{figure}[H]
      \includegraphics[width=0.8\linewidth]{model_outputs.pdf}
      \caption{Response of channel width (a), hydraulic diameter (b),  Reynolds number  (c),  water velocity (d), shear-stress (e), and width-integrated shear-stress (f)  to different water discharge values. The glacial system is in blue and the subaerial system is in green.  Horizontal bars in d, e, and f represent the range of values in the  output. Gray space represents water discharge below the mean value. }
      \label{fig:model_outs}
    \end{figure}
  \end{center}

@@

  \begin{center}
    \begin{figure}[H]
      \includegraphics[width=0.8\linewidth]{multi_run.pdf}
      \caption{Ratio of range of water velocity, shear-stress, and width integrated shear-stress for glacial and subaerial systems in response to mean water discharge (a, b, c), and  variability in water discharge (d, e, f).  
        Range  $\chi$ for each variable is given in Equation~\ref{eq:var}. Values greater than $1$ shown in white space are parameter combinations that vary more in a subglacial  system.
        Histograms (g-i) show the frequency of relative variations across variables in the parameterization.}
      \label{fig:range}
    \end{figure}
  \end{center}

@@

  Records of sediment discharge have been used to establish the relationship, or lack thereof, between sediment discharge and climate in glacial systems \cite<e.g.>[]{koppes2009a,willenbring2016,mariotti2021}.
  The variability in subglacial sediment transport capacity presented here applies most generally to short-time scales responsible for the size of subglacial channels.
  Yet, identifying climatic signals in sediment transport from transport-limited glaciers may require higher thresholds of climatic perturbation compared to subaerial systems \cite{tofelde2021}.
  This higher threshold of climatic perturbation may persist in addition to the stochastic nature of erosion and deposition in fluvial environments \cite{castletort2003,jerolmack2010,romans2016}.
  For instance, sediment discharge records from two glaciers in the Swiss Alps show that $40$ to $50$\% of a season's sediment discharge occurs when water discharge is below the $75^{\mathrm{th}}$ quantile of the season \cite{delaney2018}.
  Such a large quantity of sediment transported at lower water discharges may occur in part because sediment transport capacity responds to the size of the glacier conduit, in addition to water discharge (Section~\ref{sect:sub_mode}).

@@

  These different characteristics between glacial and subaerial channels show that records of sediment transport downstream of glaciers represent both subglacial and subaerial processes together.
  Divergent processes discussed here might be particularly relevant at glacier margins, where water transitions from pressurized subglacial flow to open-channel subaerial flow.
  The inconsistent response of sediment transport in subglacial and subaerial systems to changing water discharge could add uncertainty in evaluating  sediment transport signals in subglacial systems.
  In addition, the subglacial parameterization shows that sediment transport capacity in glacier systems responds to a large number of factors such as channel size, ice thickness, and glacier surface slope, which may react to climate forcing differently than water discharge alone. 
  The differences in subglacial and subaerial channels' response to changing hydrology should be considered when examining sediment transport processes in glacierized catchments.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% 
% \bibliography{<name of your .bib file>} don't specify the file extension
% 
% don't specify bibliographystyleiz

@@

\begin{thebibliography}{}

@@

\bibitem [\protect \citeauthoryear {%
Castelltort%
\ \BBA {} {Van Den Driessche}%
}{%
Castelltort%
\ \BBA {} {Van Den Driessche}%
}{%
{\protect \APACyear {2003}}%
}]{%
castletort2003}
\APACinsertmetastar {%
castletort2003}%
\begin{APACrefauthors}%
Castelltort, S.%
\BCBT {}\ \BBA {} {Van Den Driessche}, J.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2003}{}{}.
\newblock
{\BBOQ}\APACrefatitle {{How plausible are high-frequency sediment supply-driven
  cycles in the stratigraphic record?}} {{How plausible are high-frequency
  sediment supply-driven cycles in the stratigraphic record?}}{\BBCQ}
\newblock
\APACjournalVolNumPages{Sedimentary Geology}{157}{1}{3-13}.
\newblock
\begin{APACrefDOI} \doi{10.1016/S0037-0738(03)00066-6} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\bibitem [\protect \citeauthoryear {%
Williams%
}{%
Williams%
}{%
{\protect \APACyear {1989}}%
}]{%
williams1989}
\APACinsertmetastar {%
williams1989}%
\begin{APACrefauthors}%
Williams, G\BPBI P.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{1989}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Sediment concentration versus water discharge during
  single hydrologic events in rivers} {Sediment concentration versus water
  discharge during single hydrologic events in rivers}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Journal of Hydrology}{111}{1}{89 -- 106}.
\newblock
\begin{APACrefDOI} \doi{10.1016/0022-1694(89)90254-0} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\begin{center}
  \begin{figure}[H]
    \includegraphics[width=0.8\linewidth]{multi_run_vars.pdf}
    \caption{Variability $\chi$ in velocity ($v_g$, $v_f$; a) shear stress ($\tau_g$, $\tau_f$; b) and width-integrated shear stress ($\tau_{tg}$, $\tau_{tf}$; c)  in glacial and subaerial systems. Values are determined from examining the same parameter space in Figure~\ref{fig:range}. }
    \label{fig:gammas}
  \end{figure}
\end{center}
